---
title: "My dividend income"
author: "JNW"
description: "stuff"
date: "2023-08-08"

---

**The KarambolageNed portfolio dividends**

## Introduction

This site gives a brief overview about my dividend income and it's values are updated automatically via scripting. The Plot the data represents the amount of received dividends of the last year.

```{r}
#| echo: false
#| output: false
#| include: false

library(dplyr)
library(tidyquant)
library(quantmod)
library(ggplot2)
library(tidyverse)
library(tidyquant)
library(plotly)
library(googlesheets4)
library(readxl)

```

```{r}
#| warning: false
#| echo: false
#| output: false
#| include: false

#get dividends
#get data from the Google sheets 
#portfolio_df <- read_excel("data/2023_08_NedPortfolio.xlsx")
#portfolio_df <- portfolio_df%>% filter(!is.na(Kaufkurs))
#portfolio_df$real_time_dividend_local_currency <- NA
#portfolio_df$real_time_dividend_worth_EUR <- NA
#portfolio_df$Wertunterschied <- NA
#portfolio_df$real_time_price_local_currency <- NA
#portfolio_df$dividends_per_year <- NA

#get transition course 
# Define the currency pair
start_date <- Sys.Date() - 1  # Get data for yesterday
end_date <- Sys.Date()

```

## Market Events and Performance

The performance of the S&P 500 is subject to various market events, including economic data releases, corporate earnings reports, geopolitical developments, and central bank decisions. Market fluctuations in the S&P 500 can have a cascading effect on other financial markets and impact investor confidence.

## Long term predictions

For this point, I want to demonstrate two scenarios:

-1. scenario: weak outlook and an average growth of 3% while adding 10k per year

-2. scenario: perfect wealth generation conditions with a growth of 10% while adding 10k per year

Let's take a look at both:

1.  scenario: growth 3% p.a., 10k additional investment from the job income

2.  scenario: growth 10% p.a. + 10k additional investment from job income
