---
title: "My personal portfolio"
author: "JNW"
description: "The visualization of the KarambolageNedInvest portfolio"
date: "2023-08-10"
---

**The KarambolageNed portfolio**

# Introduction

This **portfolio** consist of a maximum of 100 values whereas the top 15 stock should compromise at least 40% of the total value.

```{r}
#| echo: false
#| output: false
#| include: false

rm(list = ls())

#load packages
library(tidyquant)
library(quantmod)
library(ggplot2)
library(tidyverse)
library(tidyquant)
library(plotly)
library(readxl)
library(gt)
library(reshape)
```

```{r}
#| warning: false
#| echo: false
#| output: false
#| include: false

#get dividends
#get data from the Google sheets 
portfolio_df <- read_excel("data/2023_08_NedPortfolio.xlsx")
portfolio_df <- portfolio_df%>% filter(!is.na(Kaufkurs))
portfolio_df$real_time_price_EUR <- NA
portfolio_df$real_time_worth_EUR <- NA
portfolio_df$Wertunterschied <- NA
portfolio_df$real_time_price_local_currency <- NA

#get transition course 
# Define the currency pair
start_date <- Sys.Date() - 1  # Get data for yesterday
end_date <- Sys.Date()

# Retrieve the exchange rate data
getFX("EUR/USD", from = start_date, to = end_date)
exchange_rate_data_today_EUR_USD <- as.vector(EURUSD$EUR.USD[1]) #EUR/USD
getFX("EUR/CHF", from = start_date, to = end_date)
exchange_rate_data_today_EUR_CHF <- as.vector(EURCHF$EUR.CHF[1]) #EUR/CHF
getFX("EUR/GBP", from = start_date, to = end_date)
exchange_rate_data_today_EUR_GBP <- as.vector(EURGBP$EUR.GBP[1]) #EUR/GBp
getFX("EUR/AUD", from = start_date, to = end_date)
exchange_rate_data_today_EUR_AUD <- as.vector(EURAUD$EUR.AUD[1]) #EUR/AUD
getFX("EUR/CNY", from = start_date, to = end_date)
exchange_rate_data_today_EUR_CNY <- as.vector(EURCNY$EUR.CNY[1]) #EUR/CNY
getFX("EUR/HKD", from = start_date, to = end_date)
exchange_rate_data_today_EUR_HKD <- as.vector(EURHKD$EUR.HKD[1]) #EUR/HKD
getFX("EUR/SGD", from = start_date, to = end_date)
exchange_rate_data_today_EUR_SGD <- as.vector(EURSGD$EUR.SGD[1]) #EUR/SGD
getFX("EUR/NOK", from = start_date, to = end_date)
exchange_rate_data_today_EUR_NOK <- as.vector(EURNOK$EUR.NOK[1]) #EUR/NOK


#loop
for(i in 1:nrow(portfolio_df)) {
   
  if(is.na(portfolio_df$Yahoo_3_letter[i])) next
  
  x1 <- tq_get(portfolio_df$Yahoo_3_letter[i], get = "stock.prices", from = start_date, to = end_date)
  x1 <- x1$adjusted

  portfolio_df$real_time_price_local_currency[i] <- x1
  
  if(portfolio_df$currency[i] == "EUR") {portfolio_df$real_time_price_EUR[i] <- x1}
  if(portfolio_df$currency[i] == "USD") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_USD} #USD
  if(portfolio_df$currency[i] == "CHF") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_CHF}
  if(portfolio_df$currency[i] == "GBP") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_GBP} 
  if(portfolio_df$currency[i] == "CNY") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_CNY} 
  if(portfolio_df$currency[i] == "SGD") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_SGD} 
  if(portfolio_df$currency[i] == "AUD") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_AUD} 
  if(portfolio_df$currency[i] == "NOK") {portfolio_df$real_time_price_EUR[i] <- x1/exchange_rate_data_today_EUR_NOK} 

#corrections
portfolio_df$real_time_price_EUR[39] <- portfolio_df$real_time_price_EUR[39]/1000  #BP
  
portfolio_df$real_time_worth_EUR[i] <- as.numeric(portfolio_df$Stück[i])*portfolio_df$real_time_price_EUR[i]
portfolio_df$Einstandswert[i] <- as.numeric(portfolio_df$Stück[i])*portfolio_df$Kaufkurs[i]
portfolio_df$Wertunterschied[i] <- portfolio_df$real_time_worth_EUR[i]-portfolio_df$Einstandswert[i]

}

x1 <- sum(portfolio_df$real_time_worth_EUR, na.rm = TRUE)

for(i in 1:nrow(portfolio_df)) {
  
portfolio_df$`%-Anteil`[i] <- (portfolio_df$real_time_worth_EUR[i]/x1)*100 #100 for %

}

```

```{r}
#| echo: false
#| output: false
#| include: false

#
#pie_chart <- plot_ly(
  #data = portfolio_df,
  #labels = ~ifelse(`%-Anteil` > 1, Wertpapier, ""),
  #values = ~`%-Anteil`,
  #type = "pie",
  #marker = list(line = list(width = 0), textposition = "outside"))  # Adjust textposition to "outside"
  #%>% layout(
  #title = "Portfolio Distribution",
  #showlegend = FALSE)  # This removes the legend


treemap_chart <- plot_ly(
  data = portfolio_df,
  ids = ~Wertpapier,
  labels = ~Wertpapier,
  parents = ~"Portfolio",  # Set a common parent for all entries
  values = ~`%-Anteil`,
  type = "treemap"
) %>% layout(
  title = "Portfolio Distribution (Treemap)",
  margin = list(l = 0, r = 0, b = 0, t = 40)  # Adjust the margin for better visibility
)



```

```{r}
#| echo: false
# Display the interactive 3D pie chart
#pie_chart
treemap_chart

```

## Market Events and Performance

For this point, here we assume that all values were bought at the same time. Doing this plot, there is some difficulties aligning all the stock data since some downloaded data has many missing values.

```{r}
#| warning: false
#| echo: false
#| output: false
#| include: false
#| label: performance calculation

#get transition course 
# Define the currency pair

df_portfolio_performance <- getSymbols("JNJ", src = "yahoo", from = "2018-01-01", to = end_date,auto.assign = FALSE)
df_portfolio_performance <- as.data.frame(df_portfolio_performance)
df_portfolio_performance$date <- rownames(df_portfolio_performance)
df_portfolio_performance <- df_portfolio_performance %>% select(date)

i <-1

#loop
for(i in 1:nrow(portfolio_df)) {
   
  if(is.na(portfolio_df$Yahoo_3_letter[i])) next
  
  x1 <- getSymbols(portfolio_df$Yahoo_3_letter[i], src = "yahoo",
                   from = portfolio_df$Date_of_Purchase[i], to = end_date, auto.assign = FALSE)
  
  x1 <- as.data.frame(x1[,6])
  x1$date <- rownames(x1)
  x1$year <- lubridate::year(x1$date)
  colnames(x1)[1] <- as.character(portfolio_df$Yahoo_3_letter[i])
  
  x1$real_time_price_local_currency <- x1[,1]
  x2 <- portfolio_df$currency[i]
  
  if(x2 == "EUR") {x1[,1] <- x1[,1]}
  if(x2 == "USD") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_USD}
  if(x2 == "CHF") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_CHF}
  if(x2 == "GBP") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_GBP} 
  if(x2 == "CNY") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_CNY} 
  if(x2 == "SGD") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_SGD} 
  if(x2 == "AUD") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_AUD} 
  if(x2 == "NOK") {x1[,1]  <- x1[,1]/exchange_rate_data_today_EUR_NOK} 



x1[,1] <- as.numeric(portfolio_df$Stück[i])*x1[,1]

if(i == 39) {x1[,1] <- x1[,1]/1000} # BP

message(i)
#combine with left_join
df_portfolio_performance <- left_join(df_portfolio_performance, 
                                      x1 %>% select(1:2), by= "date")
  
}
 
df_portfolio_performance$year <- lubridate::year(df_portfolio_performance$date)



# If you want to add the sum as a new column to the selected DataFrame
df_portfolio_performance$Total_Sum <- rowSums(df_portfolio_performance[2:(ncol(df_portfolio_performance)-2)], na.rm = TRUE)


df_portfolio_performance$Total_Sum_entries <- rowSums(!is.na(df_portfolio_performance[2:(ncol(df_portfolio_performance)-2)]))


```

```{r}
#| echo: false
#| output: false
#| include: false


#subset
for (i in 1:(nrow(df_portfolio_performance)-1)) {

if(df_portfolio_performance$Total_Sum_entries[i]>df_portfolio_performance$Total_Sum_entries[i+1]) {df_portfolio_performance[-c(i+1,i+2,i+3,i+4),]}
  message(i)
}


# Create the smoothed line plot
line_plot <- plot_ly(df_portfolio_performance, x = ~date, y = ~Total_Sum, type = 'scatter', mode = 'lines')

i <- 96

```

```{r}
#| echo: false
# Display the interactive 3D pie chart
line_plot

```

Calculating the performance is tough since the money invested changes from to month due to the additional savings etc.

## Long term predictions

For this point, I want to demonstrate two scenarios:

-1. scenario: weak outlook and an average growth of 3% while adding 10k per year

-2. scenario: perfect wealth generation conditions with a growth of 10% while adding 10k per year

-3. scenario: once 200k accumulation and 5% growth

Let's take a look at both:

```{r}
#| echo: false
#| output: false
#| include: false

# Create a vector of years from 1 to n (where n is the number of years you want to calculate)
years <- 0:30  # You can adjust this to the number of years you want

# Calculate the values for each year based on the growth rate and additional amount
initial_amount <- 200000
growth_rate_1 <- 0.03  # 3% expressed as a decimal
growth_rate_2 <- 0.05  # 3% expressed as a decimal
growth_rate_3 <- 0.10  # 3% expressed as a decimal

additional_amount <- 10000

# Calculate the values for each year
values_1 <- initial_amount * (1 + growth_rate_1)^years + additional_amount * years
values_2 <- initial_amount * (1 + growth_rate_2)^years + additional_amount * years
values_3 <- initial_amount * (1 + growth_rate_3)^years + additional_amount * years


# Create a dataframe
growth_df <- data.frame(Year = years, Value_1 = values_1, 
                        Value_2 = values_2, 
                        Value_3 = values_3)

# Create a line plot using Plotly
plot <- plot_ly(growth_df, x = ~Year, type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~Value_1, name = 'Scenario 1', text = ~paste("Year: ", Year, "<br>Value: EUR", round(Value_1, 0))) %>%
  add_trace(y = ~Value_2, name = 'Scenario 2', text = ~paste("Year: ", Year, "<br>Value: EUR", round(Value_2, 0))) %>%
  add_trace(y = ~Value_3, name = 'Scenario 3', text = ~paste("Year: ", Year, "<br>Value: EUR", round(Value_3, 0))) %>%
  layout(title = "Investment Growth Over Time with 3 different scenarios",
         xaxis = list(title = "Year after Initial investment"),
         yaxis = list(title = "Investment Value"))


```

```{r}
#| output: true
#| echo: false

plot

```

Looking at this plot, I realized two things: First, an initial investment of 200k makes you a millionaire most likely over 30 years(with inflation adjustment most likely nothing special). And secondly, stock return and higher growth rate (green) outcompetes a lower performance and additional investments (orange line).

## Additional thoughts

The goal is not retire as fast as possible. Live without work is damn boring.

## Portfolio as table

```{r}
#| echo: false
#| output: false
#| include: false

#install.packages("gtExtras")
#length(ls.str('package:gtExtras', mode='function'))
library(gtExtras)
library(tidyverse)
library(gt)
library(markdown)
```

```{r}
#| echo: false
#| output: true
#| include: true
#| warning: false


portfolio_df %>%
  select(Wertpapier, real_time_price_EUR, Kaufkurs, real_time_worth_EUR, Notiz) %>%
  mutate_at(vars(real_time_price_EUR, Kaufkurs, real_time_worth_EUR), ~ round(., 2)) %>%
  gt() %>%
  tab_header(title = "Portfolio as Table", subtitle = "Price in EUR instead of USD") %>%
  cols_label(Wertpapier = "Identifier", real_time_worth_EUR = "Value",  real_time_price_EUR = "Current Price", Kaufkurs = "Buying Price") 


```
